XXXXX

### 2014-09-26 paper/paper1.tex
R-44-PATTERN-MATCHING-ON-RDF-LITERALS

>>>>

A social security number is a string that matches the given regular expression. 
The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
The first axiom explicitly declares :SSN to be a datatype. 
The datatype :SSN can be used just like any other datatype; 
for example, it is used in the third axiom to define the range of the :hasSSN property.
